---
title: "Final Project"
author: "Luke Geel"
date: "11/25/2020"
output: html_document
---
combined attacks worldwide
```{r}
library(tidyverse)


globalterrorismdb_0718dist %>%
  filter (!is.na(nkill)) %>% 
  group_by(iyear) %>%
  summarise(num_deaths = sum(nkill)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=num_deaths)) +
  labs(x= "year", y="total deaths")

globalterrorismdb_0718dist %>%
  filter (!is.na(nkill)) %>% 
  group_by(iyear) %>%
  summarise(num_attacks = n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=num_attacks)) +
  labs(x="year",y="number of attacks")

globalterrorismdb_0718dist %>%
  filter (!is.na(nkill)) %>% 
  group_by(iyear) %>%
  summarise(avg_kill_per_attack = sum(nkill)/n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=avg_kill_per_attack)) +
  labs(x="year",y="average deaths per attack")
```

How has terrorism changed over the year
proportion of different attacks over the years
```{r}
globalterrorismdb_0718dist %>%
  filter(attacktype1_txt != "Unknown") %>%
  filter(iyear != "1993") %>%
  ggplot(aes(x=iyear, fill=attacktype1_txt)) +
  geom_bar(position = "fill") + 
  labs(x="year",y="proportion of attacks") 
```
proportion of places attacked over the years
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  filter(attacktype1_txt != "Unknown") %>%
  filter(iyear != "1993") %>%
  ggplot(aes(x=iyear, fill=newreg)) +
  geom_bar(position = "fill") +
  labs(x="year", y="proportion")
```
proportion of violent attacks over the years
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$deathscat[nkill == 0] <- "0 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 1 & nkill <= 3] <- "1-3 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 4 & nkill <= 10] <- "4-10 deaths"
globalterrorismdb_0718dist$deathscat[nkill > 10] <- "10+ deaths"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "Asia") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))


globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "Australia & Oceania") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "Europe") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "Sub-Saharan Africa") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "North America") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "South America") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))

globalterrorismdb_0718dist %>%
  group_by(iyear, newreg) %>%
  filter(newreg == "Middle East & North Africa") %>%
  filter(!is.na(nkill)) %>%
  filter(iyear != 1993) %>%
  ggplot(aes(x=iyear, fill=deathscat)) +
  geom_bar(position = "fill") +
  facet_grid(~newreg)+
  scale_x_continuous(breaks=seq(1970,2010,20))
```
total deaths per region over years
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$deathscat[nkill == 0] <- "0 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 1 & nkill <= 3] <- "1-3 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 4 & nkill <= 10] <- "4-10 deaths"
globalterrorismdb_0718dist$deathscat[nkill > 10] <- "10+ deaths"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"



globalterrorismdb_0718dist %>%
  filter(!is.na(nkill)) %>%
  group_by(newreg, iyear) %>%
  summarize(kills = sum(nkill)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=kills, color = newreg))
```
average kills per attack per region over
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$deathscat[nkill == 0] <- "0 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 1 & nkill <= 3] <- "1-3 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 4 & nkill <= 10] <- "4-10 deaths"
globalterrorismdb_0718dist$deathscat[nkill > 10] <- "10+ deaths"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"



globalterrorismdb_0718dist %>%
  filter(!is.na(nkill)) %>%
  group_by(newreg, iyear) %>%
  summarise(avg_kills = sum(nkill)/n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=avg_kills, color = newreg))
```
Number of attacks over months
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$deathscat[nkill == 0] <- "0 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 1 & nkill <= 3] <- "1-3 deaths"
globalterrorismdb_0718dist$deathscat[nkill >= 4 & nkill <= 10] <- "4-10 deaths"
globalterrorismdb_0718dist$deathscat[nkill > 10] <- "10+ deaths"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  filter(imonth != 0) %>%
  group_by(imonth, newreg) %>%
  summarise(attacks_per_month = n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=imonth, y=attacks_per_month, color = newreg))
  
```
How criteria is different for reach region
not working
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 1 & crit3 == 1] <- " POLITICAL, ECONOMIC, RELIGIOUS, OR SOCIAL GOAL + INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S) + OUTSIDE INTERNATIONAL HUMANITARIAN LAW"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 0 & crit3 == 0] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR SOCIAL GOAL"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 1 & crit3 == 0] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR SOCIAL GOAL + INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S)"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 0 & crit3 == 1] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR SOCIAL GOAL + OUTSIDE INTERNATIONAL HUMANITARIAN LAW" 
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 1 & crit3 == 1] <- "INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S) + OUTSIDE INTERNATIONAL HUMANITARIAN LAW" 
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 1 & crit3 == 0] <- "INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S)"
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 0 & crit3 == 1] <- " OUTSIDE INTERNATIONAL HUMANITARIAN LAW"
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 0 & crit3 == 0] <- " UNKNOWN"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>% 
  filter(newreg == "North America") %>%
  ggplot(aes(x=iyear, fill = multiple)) +
  geom_bar(position = "fill")
  


```
deaths/attacks in top 10 most attacked states
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 1 & crit3 == 1] <- " POLITICAL, ECONOMIC, RELIGIOUS, OR
SOCIAL GOAL + INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S) + OUTSIDE INTERNATIONAL
HUMANITARIAN LAW"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 0 & crit3 == 0] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR
SOCIAL GOAL"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 1 & crit3 == 0] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR
SOCIAL GOAL + INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S)"
globalterrorismdb_0718dist$newcrit[crit1 == 1 & crit2 == 0 & crit3 == 1] <- "POLITICAL, ECONOMIC, RELIGIOUS, OR SOCIAL GOAL + OUTSIDE INTERNATIONAL HUMANITARIAN LAW" 
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 1 & crit3 == 1] <- "INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S) + OUTSIDE INTERNATIONAL HUMANITARIAN LAW" 
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 1 & crit3 == 0] <- "INTENTION TO COERCE, INTIMIDATE OR PUBLICIZE TO LARGER AUDIENCE(S)"
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 0 & crit3 == 1] <- " OUTSIDE INTERNATIONAL HUMANITARIAN LAW"
globalterrorismdb_0718dist$newcrit[crit1 == 0 & crit2 == 0 & crit3 == 0] <- " UNKNOWN"
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  filter(!is.na(nkill)) %>%
  filter(provstate != "Unknown") %>%
  group_by(provstate) %>% 
  summarize(killed = sum(nkill)) %>%
  arrange(desc(killed)) %>%
  slice(1:10)

globalterrorismdb_0718dist %>%
  filter(!is.na(nkill))%>%
  filter(provstate == c("Baghdad", "Nineveh", "Borno", "Al Anbar", "Saladin", "Diyala", "Eastern", "Northern", "Punjab", "Federally Administered Tribal Areas") ) %>% 
  group_by(provstate, iyear) %>% 
  summarise(killed_per_year = sum(nkill)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y= killed_per_year, color = provstate))

 globalterrorismdb_0718dist %>%
  filter(!is.na(nkill))%>%
  filter(provstate == c("Baghdad", "Nineveh", "Borno", "Al Anbar", "Saladin", "Diyala", "Eastern", "Northern", "Punjab", "Federally Administered Tribal Areas") ) %>% 
  group_by(provstate, iyear) %>% 
  summarise(attacks_per_year = n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y= attacks_per_year, color = provstate)) 
```
attacks in top 10 most attacked countries
```{r}
globalterrorismdb_0718dist %>%
  filter(!is.na(nkill)) %>%
  filter(country_txt != "Unknown") %>%
  group_by(country_txt) %>% 
  summarize(killed = sum(nkill)) %>%
  arrange(desc(killed)) %>%
  slice(1:10)

globalterrorismdb_0718dist %>%
  filter(!is.na(nkill))%>%
  filter(country_txt == c("Iraq", "Afghanistan", "Pakistan", "Nigeria", "India", "Sri Lanka", "Syria", "Colombia", "Peru", "El Salvador") ) %>% 
  group_by(country_txt, iyear) %>% 
  summarise(killed_per_year = sum(nkill)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y= killed_per_year, color = country_txt))

globalterrorismdb_0718dist %>%
  filter(!is.na(nkill))%>%
  filter(country_txt == c("Iraq", "Afghanistan", "Pakistan", "Nigeria", "India", "Sri Lanka", "Syria", "Colombia", "Peru", "El Salvador") ) %>% 
  group_by(country_txt, iyear) %>% 
  summarise(attacks_per_year = n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y= attacks_per_year, color = country_txt))

globalterrorismdb_0718dist %>%
  filter(!is.na(nkill))%>%
  filter(country_txt == c("Iraq", "Afghanistan", "Pakistan", "Nigeria", "India", "Sri Lanka", "Syria", "Colombia", 
  "Peru", "El Salvador") ) %>% 
  group_by(country_txt, iyear) %>% 
  summarise(avg_killed_per_attack = sum(nkill)/n_distinct(eventid)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y= avg_killed_per_attack, color = country_txt))

```
catastrophic property damage
```{r}
globalterrorismdb_0718dist %>%
  filter(propextent == 1)
```
total property damage value
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  filter(!is.na(propvalue)) %>%
  group_by(newreg, iyear) %>%
  summarize(total_damage = sum(propvalue)) %>%
  ggplot() +
  geom_line(aes(x=iyear, y=total_damage, color = newreg))
```
different categories of property damage 
```{r}
attach(globalterrorismdb_0718dist)
globalterrorismdb_0718dist$newreg[region_txt == "Australasia & Oceania"] <- "Australia & Oceania"
globalterrorismdb_0718dist$newreg[region_txt == "Central America & Caribbean"] <- "Central America & Caribbean"
globalterrorismdb_0718dist$newreg[region_txt == "Central Asia" | region_txt == "East Asia" | region_txt == "South Asia" | region_txt == "Southeast Asia"] <- "Asia"
globalterrorismdb_0718dist$newreg[region_txt == "Eastern Europe" | region_txt == "Western Europe"] <- "Europe"
globalterrorismdb_0718dist$newreg[region_txt == "Middle East & North Africa"] <- "Middle East & North Africa"
globalterrorismdb_0718dist$newreg[region_txt == "North America"] <- "North America"
globalterrorismdb_0718dist$newreg[region_txt == "South America"] <- "South America"
globalterrorismdb_0718dist$newreg[region_txt == "Sub-Saharan Africa"] <- "Sub-Saharan Africa"

globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "North America") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "North America")
  
globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "Middle East & North Africa") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "Middle East & North Africa")
  
globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "Asia") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "Asia")

globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "Europe") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "Europe")

globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "Sub-Saharan Africa") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "Sub-Saharan Africa")

globalterrorismdb_0718dist %>%
  filter(propextent_txt != "Unknown") %>%
  filter(newreg == "Australia & Oceania") %>%
  ggplot(aes(x=iyear, fill = propextent_txt)) +
  geom_bar(position = "fill") +
  labs(title = "Australia & Oceania")
```




